Making Sequential Programs Deterministic

### 2019-04-05 introduction.tex
into edits

@@

\todo{1211 LOC of Java in the determinism checker}

>>>>

We implemented \TheDeterminismChecker as a pluggable type checker on top of the checker-framework available at \href{https://checkerframework.org/}{https://checkerframework.org/}. \TheDeterminismChecker is written in Java and
spans approximately 1.2K lines of code.

@@
